Maps

### 2016-03-21 108-mapping.Rmd
Revert "Count number of sections for comparison to NY"
This reverts commit 04e65feb331d6ff53c08180debbcdb255e4a7cd2.

regions <- read_csv("regions.csv")

map_matches_sections <- map_matches %>% 
  filter(borrower_year >= match_year) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup() %>%  
  filter(score >= 0.2) %>% 
  count(borrower_code) %>% 
  mutate(year = extract_date(borrower_code)) %>% 
  mutate(state = extract_state(borrower_code)) %>% 
  left_join(regions)

@@

map_summary <- map_matches %>% 
  # filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
  group_by(borrower_state) %>%
  summarize(score = sum(score)) %>% 
  arrange(desc(score))

@@

```{r}
library(ggrepel)
ggplot(map_matches_sections, aes(x = year, y = n, color = region, group = state)) +
  geom_point() +
  geom_line() 
    # geom_label_repel(aes(label = state))
```

>>>>

map_matches <- map_matches %>% 
  filter(borrower_year >= match_year) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup() %>%  
  filter(score >= 0.2)

@@

map_summary <- map_matches %>% 
  filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
  group_by(borrower_state) %>% 
  summarize(score = mean(score)) %>% 
  arrange(desc(score))

@@
